Differences in Chinese and Western tourists faced with Japanese hospitality: A natural language processing approach

### 2021-02-15 1_manuscript/itt-emotion.tex
Added 2nd half corrections after checking, have to checkout to look for V5 since it got deleted

  \subsection{Experiment results and answering research questions}

    Our research questions were about two things. In research questions \ref{rsq:hospitality} and \ref{rsq:hospitality_both}, we decide that the objective of this study to determine how Chinese and Western tourists interact with the \textit{omotenashi} culture influenced hospitality and service in Japan, and how are they different in their perceptions in this matter. We observed the top-ranking positive factors for Chinese tourists across different price ranges in Table \ref{tab:freq_res_pos}, and specifically the word ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' and its pairings in Table \ref{tab:adj_zh_pos}. From these observations, we can infer that, while service, cleanliness, and breakfast are praised in most hotels, location is usually placed above it in importance on the pairings. When we see the rest of the factors lower on the list, we see that the list is more populated with hard attributes like location and transportation availability across different price ranges. From the negative keyword usages in Table \ref{tab:freq_res_neg}, there are complaints about the lack of a Chinese friendly environment. However, most complaints are also about hard attributes such as the building's age and the distance from other convenient spots. Nevertheless, the most complained about aspect is the price of the hotel. Surprisingly, all of the price ranges have this negative keyword at the top of the list, suggesting that it is the main concern to Chinese customers with different travel purposes.

    On the other hand, the word ``staff'' is the second or third in the lists of satisfaction factors in English-written reviews in all the price ranges. This word is followed by a few other keywords lower in the top 10 list, such as ``helpful'' or ``friendly''. When we look at the pairings of the top-ranked keyword ``good'' in Table \ref{tab:adj_en_pos}, we find that customers mostly praise the location, service, breakfast, or English availability. When we look at the negative keyword ``poor'' and its pairings in Table \ref{tab:adj_en_neg}, we see that it is also service-related concepts that the Western tourists are disappointed with. With these results, we can observe that both Chinese and English-speaking tourists in Japan have different priorities. However, both populations consider the hotel's location and transport availability (subways and trains) nearby as secondary but still essential points in their satisfaction with a hotel. The Chinese customers are primarily satisfied with the room quality in spaciousness and cleanliness and the service of breakfast.

    In contrast, the English-speaking customers are easily upset by any lack of cleanliness and smoke smell from cigarettes. Surprisingly, the cigarette smell is an issue even in the middle to high-class hotels above 30,000 yen per night. However, above 50,000 yen per night, this problem seems to disappear from the list of top 10 concerns. Old and dated buildings seem to be a concern for both populations. On the positive side, for all price ranges considered, English-speaking tourists value staff friendliness over room quality when considering their satisfaction. In contrast, Chinese tourists consider location and transportation more often.

    We also can observe some keywords that are not considered by their counterparts. For example, English-speaking customers mentioned tobacco smell in many reviews. However, it was not statistically identified as a problem for their Chinese counterparts. On the other hand, while it appears in both English and Chinese lists, references to ``\begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)'' are more common in the Chinese lists across hotels of 15,000 yen to 200,000 yen per night. Meanwhile, the term ``shopping'' only appears in the 20,000 to 30,000 yen per night top 10 positive keywords list for English-speakers.

    In our research questions \ref{rsq:hard_soft} and \ref{rsq:hard_soft_diff}, we ponder how customers of both cultural backgrounds evaluate hard and soft attributes of the hotel and how they differ in those evaluations. Here we define hard attributes as those relating to the hotel's physical, structural, or environmental aspects. These are often impossible or impractical to change by the hotel management and staff, such as facilities, infrastructure, the surroundings, view, or location convenience. On the other hand, hotel staff and management can change soft attributes, for example, by improving the hotel's services via training or hiring specialized staff, improving the quantity or quality of amenities, bedsheets, or general cleanliness. Our study found that Chinese tourists are mostly positively reacting more to the hotel's hard attributes. There is a slightly hard leaning (53\%) concern with hard attributes in negative sentences, albeit this is more uniform than the positive evaluations. English-speaking tourists, on the other hand, are both positively and negatively more responsive to soft attributes. In the case of negative keywords, English-speaking tourists are overwhelmingly more concerned with the hotel's soft attributes dissatisfaction somehow.

    One factor that both populations have in common is, when perceiving the hotel negatively, ``\begin{CJK}{UTF8}{gbsn}老\end{CJK} (old)'', ``dated'', ``outdated'', or ``\begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete)'' aspects of the room or the hotel are being criticized across, surprisingly, most price ranges. This is, however, a hard attribute and is unlikely to change for most hotels.

  \subsection{Chinese tourists - A big and clean space}\label{disc:zh}

    We found that mainland Chinese tourists are satisfied mostly by Japanese hotels' big and clean spaces. From the adjectival pairings that we extracted with dependency parsing and POS tagging in Table \ref{tab:adj_zh_pos}, we can observe that mostly they mean big and clean rooms. Other mentions are also big markets nearby or a big bed. We can observe that across different price ranges, the usage of the word ``\begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)'' increases as the hotel increases in price. However, we can see that they still react positively in a significant manner in cheaper hotels. Inspecting closer by taking random samples of the pairs of ``\begin{CJK}{UTF8}{gbsn}大 空间\end{CJK} (big space)'' or ``\begin{CJK}{UTF8}{gbsn}大 面积\end{CJK} (large area)'', we can see that there are also many references to the public bathing facilities in the hotel. We can also see them mentioned as a word pairing ``\begin{CJK}{UTF8}{gbsn}棒 温泉\end{CJK} (great hot spring)''. In Japan, there is what is called ``\begin{CJK}{UTF8}{min}銭湯\end{CJK} (\textit{sent\=o})'', which are artificially made public bathing facilities, on occasions including saunas and baths with unique qualities. On the other hand, there are natural hot springs, called ``\begin{CJK}{UTF8}{gbsn}温泉\end{CJK} (\textit{onsen})''. They can either be bathing in the natural source of the water or using the hot springs in artificially made bath facilities. It is a Japanese custom and culture that all customers use the facilities after cleaning themselves in a shower and go into the baths without any clothes. It can be a cultural shock for many tourists, but this is a fundamental attraction for many.

    However, the size of the room or the bed is a hard attribute. Without considering rebuilding the hotel, it is not trivial to improve on. On the other hand, cleanliness is mostly relating to soft attributes when we observe its adjectival pairings. We can observe pairs such as ``\begin{CJK}{UTF8}{gbsn}干净 房间\end{CJK} (clean room)'' at the top rank of all price ranges, and then variably ``\begin{CJK}{UTF8}{gbsn}干净 酒店\end{CJK} (clean hotel)'', ``\begin{CJK}{UTF8}{gbsn}干净 总体\end{CJK} (clean overall)'', ``\begin{CJK}{UTF8}{gbsn}干净 环境\end{CJK} (clean environment)'', and ``\begin{CJK}{UTF8}{gbsn}干净 设施\end{CJK} (clean facilities)'', among other examples. In negative reviews, there is a mention of criticizing the ``\begin{CJK}{UTF8}{gbsn}一般 卫生\end{CJK} (general hygiene)'' of the hotel, although it is an uncommon pair. Therefore, we can assert that cleanliness is an important soft attribute for Chinese customers and that they are mostly pleased with their expectations being met.

    One key component we found in Chinese customer satisfaction soft factors is the inclusion of breakfast within the hotel. While other food-related words were extracted, most of them were general, like ``food'' or ``eating,'' which were lower ranking. In contrast, the word ``\begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)'' refers possibly to its inclusion in the hotel commodities, was frequently used in positive texts compared to other food-related words. The word ``\begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)'' is also observed across all price ranges, although at different priorities in each of them. However, we assert that it is an important factor. Observing word pairs from the positive Chinese keywords in Table \ref{tab:adj_zh_pos}, we can also see that ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' is paired as ``\begin{CJK}{UTF8}{gbsn}不错 早餐\end{CJK} (nice breakfast)'' in four of the seven price ranges with reviews available as part of the top 4 pairings. It is only slightly lower on other categories, although it is not shown on the table. Thus we consider that a recommended strategy for hotel management is to invest in the inclusion or betterment of hotel breakfast to increase good reviews.

  \subsection{Western tourists - A friendly face, and absolutely clean}\label{disc:en}

    From the satisfaction factors of English-speaking tourists, we can see that at least three words relate directly to staff friendliness and services, being ``staff'', ``helpful'' and ``friendliness'' in the general database. The word ``staff'' is the second most frequently used word for satisfied customers across most price ranges, and only third in one of them. Adding to that, ``helpful'' and ``friendly'' follow it lower in the list in most price ranges. The word ``good'' is mostly about the location, the service, breakfast, or English availability in Table \ref{tab:adj_en_pos}. Like Chinese customers, Western customers also seem to enjoy the included breakfasts regarding their satisfaction keyword pairings. However, the word does not appear directly in the top 10 list as in their Chinese counterparts. The words ``helpful'' and ``friendly'' are mostly paired with ``staff'', ``concierge'', ``desk'', and ``service''. When we look at the negative keyword ‘poor’ and its pairings in Table \ref{tab:adj_en_neg}, we see that it is also service-related concepts that the Western tourists are disappointed with when they react negatively.

    Another soft attribute that is high on the list for most of the price ranges is the word ``clean''. Since it is an adjective, we have explored the word pairings as well. Customers are mostly praising ``clean rooms'' and ``clean bathrooms'', while also referring to the hotel in general. It seems that when observing the negative keyword frequencies for English-speakers, we can find words such as ``dirty'', ``carpet'', and from the word pairings ``dirty carpet'', ``dirty room'', and ``dirty bathroom''. Along with complaints about off-putting smells, we can conclude that Western tourists have high expectations about cleanliness when traveling in Japan.

    An interesting detail of the keyword ranking is that the word ``comfortable'' is high on the satisfaction factors and ``uncomfortable'' high on the dissatisfaction factors. The words are paired with nouns like ``bed'', or ``room'', ``pillow'' or ``mattress'', generally referring to their sleep conditions in the hotel.
    It seems that Western tourists are highly sensitive to comfort levels in the hotels and whether it reaches their expectations. The ranking for the negative keyword ``uncomfortable'' is similar across most price ranges, except the two most expensive ones, where this keyword disappears from the top 10 list.

    While less high in priority, the price range of 15,000 to 20,000 yen hotels also mentions ``free'' as one of the top 10 positive keywords, paired mostly with ``wifi''. This price range is mostly for business hotels, where we infer users would be expecting this feature the most. Western tourists are highly sensitive to comfort levels in the hotels and whether it reaches their expectations.

  \subsection{Tobacco, what's that smell?}\label{disc:tobacco}

    A concern for Western tourists was the smell of tobacco in their room, which can be considered a soft attribute. Tobacco was found not only as a standalone word ``cigarette'', but also as word pairs in Table \ref{tab:adj_en_neg}. We can find other related word pairs such as ``funny smell''. Upon manual inspection of a sample of reviews with this keyword, we found that the room was often advertised as non-smoking, yet, the smell permeated the room and curtains. Another common complaint was that there were no non-smoking facilities available at all in the first place. The smell of smoke can completely ruin some customers’ stay and give a bad impression to review writers, lowering the number of future customers.

    However, in comparison, Chinese customers seem not to be bothered by this at all. We consulted studies involving the use of tobacco in different countries. Previous research states that 49 - 60\% of Chinese men (and 2.0 - 2.8\% of women) currently smoke or have smoked before. This was taken from a sample of 170,000 Chinese adults in 2013-2014, which is high compared to many English-speaking countries \cite[][]{zhang2019tobacco,who2015tobacco}.

    Japan has a polarized view on the topic of smoking. Despite being one of the world’s largest tobacco markets, its use has decreased in recent years. Smoking in public spaces is prohibited in some wards of Tokyo (namely Chiyoda, Shinjuku, and Shibuya). However, it is generally only urged and not mandatory to have smoking restrictions in restaurants, bars, hotels, and public areas. However, many places have designated smoking rooms are available to keep the smoke in an enclosed area and avoid bothering others. Despite this, businesses, especially those who cater to certain customers, will generally be discouraged from having smoking restrictions if they want to keep their clientele. If Japanese hotels want to cater to all kinds of customers, Western and Asian alike, they must provide spaces without tobacco smell. After all, even if it does not bother a few customers, the lack of smell would make it an appropriate space for all customers.

@@

    The hotel's location, closeness to the subway and public transport, and nearby shops' availability were observed to be of importance to both Chinese and English-speaking tourists. In positive word pairings Tables \ref{tab:adj_zh_pos} and \ref{tab:adj_en_pos}, we can find pairs such as ``\begin{CJK}{UTF8}{gbsn}不错 位置\end{CJK} (nice location)'', ``\begin{CJK}{UTF8}{gbsn}近 地铁站\end{CJK} (near subway station)'', ``\begin{CJK}{UTF8}{gbsn}近 地铁\end{CJK} (near subway)'' in Chinese texts and ``good location'', ``great location'', and ``great view'', as well as single keywords ``location'' and ``shopping'' for English-speakers, and ``\begin{CJK}{UTF8}{gbsn}交通\end{CJK} (traffic)'', ``\begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)'', ``\begin{CJK}{UTF8}{gbsn}地铁\end{CJK} (subway)'', and ``\begin{CJK}{UTF8}{gbsn}环境\end{CJK} (environment or surroundings)'' for Chinese speakers. All of these keywords and their location in each population's priorities across the price ranges signal that while it was not the priority for either of them, the hotel's location is a secondary but still important point in the hotel's satisfaction. However, since this is a hard attribute, unchangeable to the hotel's management, it is not often considered in the literature. Upon inspection of examples from the data, we found that most customers were satisfied if the hotel was near to at least two other subjects: subway, train, and convenience stores.

    Japan is a country with a peculiar public transport system. The rush hour makes for a subway filled to the brim with people in suits making their commute, and trains and subway stations in Tokyo create a confusing public transport map for a visitor. Buses are also available, although less used than the rail systems in the big cities. These three are unusually affordable in price. Then there are the more expensive transports, such as the bullet train \textit{shinkansen} for traveling across the country, and taxis. Taxis in Japan are a luxury compared to other countries. In less developed countries, a taxi is the cheap method of transport of choice. In Japan, taxis are made to provide a high-quality experience with a matching price. This means that for tourists, subway availability and maps or GPS applications and a plan to travel the city are of utmost necessity.

    Japanese convenience stores, on the other hand, are also famous worldwide. Japanese convenience stores are a haven for the traveler in need. It offers anything, from drinks and snacks to full meals, copy and scanning machines, alcohol, cleaning supplies, personal hygiene items, underwear, towels, international ATMs, among other things. If some trouble occurred, or a traveler forgot to pack a particular item, it is almost sure that they can find it.

    Therefore, considering that both transport systems and nearby shops are points of interest for Chinese and Western tourists, Japanese hotels have to carefully choose their location from the moment they are constructed. While not a top priority, this is a universal factor for both customer groups, and it can be an instant way to generate positive reviews.

@@

  Below we explore the possible interactions with Japanese hospitality, the differences between Chinese and Western tourists, the possible cause for them, how they vary across different price ranges, and what they imply for the industry. We also discuss the differences between the hotel's hard and soft attributes and how they contribute to customers' satisfaction.

@@

    To this day, scholars continue to correct our historical bias towards the west. Studies have determined that different cultural backgrounds lead to different expectations, which influences tourists' satisfaction. Meaning, tourists of a particular culture will have different leading satisfaction factors across different destinations. However, Japan presents a particular environment. The spirit of hospitality and service, \textit{omotenashi}, excels and is considered the highest standard across the world. Can such an environment affect different cultures equally? Or is it only attractive to certain cultures? Our study brings light to these questions.

    Our results indicate that out of the two, Western tourists are the most satisfied with soft attributes, such as friendly and helpful staff in Japan. As explained earlier in this paper, Japan is famous for its customer service all over the world. Respectful language and bowing are not exclusive to high priced hotels or businesses. These can even be found in convenience stores. The level of hospitality in even the cheapest of convenience stores is starkly different from Westerner experiences. While it could be a culture shock to some, it is mostly seen positively. After all, the Japanese staff respectfully treats all customers. However, for some customers, this could be the best way they have been treated until that moment. Now, in higher priced hotels, the adjectives used to praise the service go from normal descriptors like ``good'' to higher levels of praise like ``wonderful staff'', ``wonderful experience'', ``excellent service'', and ``excellent staff''. We can also see that \cite{kozak2002} and \cite{shanka2004} have also found that hospitality and staff friendliness is a vital determinant in Western tourists' satisfaction.

    However, we can see from the negative English keywords that a big part of the dissatisfaction with Japanese hotels stems from a lack of hygiene and room cleanliness. Although Chinese customers only had positive keywords about cleanliness, English-speaking customers have found many places unacceptable to their standards. This is particularly true at hotels below 50,000 yen per night. The most common complaint regarding cleanliness was about the carpet, followed by complaints about cigarette stench and general dirtiness. \cite{kozak2002} also found that hygiene and cleanliness were essential satisfaction determinants for Western tourists. However, in the previous literature, this was linked merely to satisfaction. In comparison, our research uncovered that words relating to cleanliness are mostly linked to dissatisfaction. Westerners could be said to have a high standard of room cleanliness when compared to their Chinese counterparts.

    According to previous research, we can see that Western tourists are already inclined to appreciate hospitality for their satisfaction. When presented with Japanese hospitality, this expectation is met and overcome. In contrast, we can see from our results that Chinese tourists had less focus on hospitality, staff, or service and were more concerned with room quality. However, when analyzing the word pairs for ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' and for ``\begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great)'', we can see that they do praise staff, service and breakfast. Observing the percentage of hard to soft attributes in Figure \ref{fig:hard_soft_zh}, however, we know that Chinese customers are satisfied more with hard attributes, compared to the Western tourists who seem to be meeting more than their expectations.

>>>>

  \subsection{Experimental results and answers to research questions}

    Our research questions were related to two issues. Based on research questions \ref{rsq:hospitality} and \ref{rsq:hospitality_both}, the objective of this study was to determine how Chinese and Western tourists respond to the \textit{omotenashi} culture, which influences hospitality and service in Japan, and the differences in their perception of this hospitality. We observed the top-ranking positive factors for Chinese tourists across different price ranges, as shown in Table \ref{tab:freq_res_pos}, and specifically the word ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' and its pairings, as shown in Table \ref{tab:adj_zh_pos}. These observations revealed that, while service, cleanliness, and breakfast were praised in most hotels, location usually placed higher in importance on the pairings. From the rest of the factors that are lower on the list, we inferred that the list was more populated with hard attributes such as location and transportation availability across different price ranges. The negative keyword usages in Table \ref{tab:freq_res_neg} indicate that there were complaints about the lack of a Chinese-friendly environment, but there were more complaints about hard attributes such as the building's age and the distance from other convenient spots. However, most complaints were about the price of the hotel, which included all of the price ranges; therefore, the price was the main concern for Chinese customers with different travel purposes.

    The word ``staff'' is the second or third in all the price ranges in the lists of satisfaction factors in reviews written in English . This word is followed by a few other keywords that are lower in the top 10 list, such as ``helpful'' or ``friendly.'' From the pairings of the top-ranking keyword ``good'' in Table \ref{tab:adj_en_pos}, we realize that customers mainly praise the location, service, breakfast, or English availability. From the negative keyword ``poor'' and its pairings in Table \ref{tab:adj_en_neg}, we deduce that  the Western tourists are also disappointed with service-related concepts. Therefore, both Chinese and English-speaking tourists in Japan have different priorities. However, both populations consider the hotel's location and transportation availability nearby (subways and trains) as secondary yet essential points to their satisfaction. The Chinese customers are primarily satisfied with the room quality in terms of the spaciousness and cleanliness as well as the service of breakfast.

    In contrast, the English-speaking customers were easily upset by uncleanliness and smoke smell from cigarettes. Cigarette smell was an issue even in the middle- and high-class hotels, of which the rooms were priced at more than 30,000 yen per night. For hotels with rooms priced above 50,000 yen per night, however, this problem seemed to disappear from the list of top 10 concerns. Furthermore, the age of the buildings was a concern for both populations. Nevertheless, for all price ranges considered, English-speaking tourists valued staff friendliness over room quality when considering their satisfaction. In contrast, Chinese tourists considered location and transportation more often.

    We can also observe some keywords that are not considered by their counterparts. For example, English-speaking customers mentioned tobacco smell in many reviews. However, it was not statistically identified as a problem for their Chinese counterparts. On the other hand, although they appear in both English and Chinese lists, references to ``\begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)'' are more common in the Chinese lists across hotels of 15,000 yen to 200,000 yen per night. Meanwhile, the term ``shopping'' appeared solely in the top 10 positive keywords list for English speakers who stayed in rooms priced 20,000–30,000 yen per night.

    For research questions \ref{rsq:hard_soft} and \ref{rsq:hard_soft_diff}, we considered how customers of both cultural backgrounds evaluated the hard and soft attributes of hotels. Here, we define hard attributes as those related to the hotel's physical, structural, or environmental aspects. These are often impossible or impractical to change by the hotel management and staff, such as facilities, infrastructure, surroundings, view, and location convenience. In contrast, hotel staff and management can change soft attributes, for example, by improving the hotel's services via training or hiring specialized staff, improving the quantity or quality of amenities, bedsheets, or general cleanliness. Our study discovered that Chinese tourists mostly positively react to the hotel's hard attributes, albeit the negative evaluations are more uniform than the positive evaluations, with a tendency of 53 \% towards hard attributes. English-speaking tourists, on the other hand, were more responsive to soft attributes, either positively or negatively. In the case of negative keywords, they were more concerned about the hotel's soft attributes.

    One factor that both populations had in common is that, when perceiving the hotel negatively, the ``\begin{CJK}{UTF8}{gbsn}老\end{CJK} (old),'' ``dated,'' ``outdated,'' or ``\begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete)'' aspects of the room or the hotel were surprisingly criticized across most price ranges. However, this is a hard attribute and is unlikely to change for most hotels.

  \subsection{Chinese tourists: A big and clean space}\label{disc:zh}

    We found that mainland Chinese tourists were mainly satisfied by big and clean spaces in Japanese hotels. The adjectival pairings extracted with dependency parsing and POS tagging (Table \ref{tab:adj_zh_pos})  imply big and clean rooms. Other mentions included big markets nearby or a big bed. Across different price ranges, the usage of the word ``\begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)'' increased with the increasing price of the hotel. However, they still reacted positively in cheaper hotels. When inspecting closer by taking random samples of the pairs of ``\begin{CJK}{UTF8}{gbsn}大 空间\end{CJK} (big space)'' or ``\begin{CJK}{UTF8}{gbsn}大 面积\end{CJK} (large area),'' we notice that there were also many references to the public bathing facilities in the hotel. Such references were also implied by a word pairing ``\begin{CJK}{UTF8}{gbsn}棒 温泉\end{CJK} (great hot spring).'' In Japan, there are the so-called ``\begin{CJK}{UTF8}{min}銭湯\end{CJK} (\textit{sent\=o}),'' which are artificially constructed public bathing facilities, including saunas and baths with unique qualities. On the other hand, there are natural hot springs, called ``\begin{CJK}{UTF8}{gbsn}温泉\end{CJK} (\textit{onsen}).'' The word ``\begin{CJK}{UTF8}{gbsn}温泉\end{CJK} (\textit{onsen})'' can be used bathing in the natural source of the water in rock baths or using the natural hot spring water in artificially made tiled bath facilities. It is a Japanese custom that all customers first clean themselves in a shower and afterward use the baths nude. It could be a cultural shock for many tourists but a fundamental attraction for many others.

    However, the size of the room or the bed is a hard attribute. Without considering rebuilding the hotel, it is not trivial to improve this attribute. In contrast, cleanliness is mostly related to soft attributes when we observe its adjectival pairings. We can observe pairs such as ``\begin{CJK}{UTF8}{gbsn}干净 房间\end{CJK} (clean room)'' at the top rank of all price ranges and thereupon ``\begin{CJK}{UTF8}{gbsn}干净 酒店\end{CJK} (clean hotel),'' ``\begin{CJK}{UTF8}{gbsn}干净 总体\end{CJK} (clean overall),'' ``\begin{CJK}{UTF8}{gbsn}干净 环境\end{CJK} (clean environment),'' and ``\begin{CJK}{UTF8}{gbsn}干净 设施\end{CJK} (clean facilities),'' among other examples. In negative reviews, there was a mention of criticizing the ``\begin{CJK}{UTF8}{gbsn}一般 卫生\end{CJK} (general hygiene)'' of the hotel, although it was an uncommon pair. Therefore, we can assert that cleanliness was an important soft attribute for Chinese customers and they were mostly pleased when their expectations were fulfilled.

    A key component found in Chinese customer satisfaction soft factors was the inclusion of breakfast within the hotel. While other food-related words were extracted, most of them were general, such as ``food'' or ``eating,'' and were lower-ranking. In contrast, the word ``\begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast),'' which possibly referred to its inclusion in the hotel commodities, was frequently used in positive texts compared to other food-related words. The word ``\begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)'' was also present in all price ranges, albeit at different priorities in each of them. For this reason, we regard it as an important factor. From the word pairs of the positive Chinese keywords in Table \ref{tab:adj_zh_pos}, we can also note that ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' is paired with ``\begin{CJK}{UTF8}{gbsn}不错 早餐\end{CJK} (nice breakfast)'' in four of the seven price ranges with reviews available as part of the top four pairings. It is only slightly lower in other categories, although it is not depicted on the table. Thus, we consider that a recommended strategy for hotel management is to invest in the inclusion or improvement of hotel breakfast to increase the number of good reviews.

  \subsection{Western tourists: A friendly face and absolutely clean}\label{disc:en}

    From the satisfaction factors of English-speaking tourists, we can see that at least three words were directly related to staff friendliness and services in the general database, ``staff,'' ``helpful,'' and ``friendliness.'' The word ``staff'' is the second most frequently used word for satisfied customers across most price ranges and only third in one of them. In addition, the words ``helpful'' and ``friendly'' follow it lower in the list in most price ranges. The word ``good'' mainly refers to the location, service, breakfast, or English availability in Table \ref{tab:adj_en_pos}. Similar to Chinese customers, Western customers also seemed to enjoy the included breakfasts regarding their satisfaction keyword pairings. However, the relevant word does not appear in the top 10 list directly, in contrast to their Chinese counterparts. The words ``helpful'' and ``friendly'' are mostly paired with ``staff,'' ``concierge,'' ``desk,'' and ``service.'' By considering the negative keyword ``poor'' and its pairings in Table \ref{tab:adj_en_neg}, we realized once again that Western tourists were disappointed with service-related concepts and reacted negatively.

    Another soft attribute that is high on the list for most of the price ranges is the word ``clean''; because this is an adjective, we also explored the word pairings. Customers largely praised ``clean rooms'' and ``clean bathrooms'' and also referred to the hotel in general. When observing the negative keyword frequencies for English speakers, we can find words such as ``dirty'' and ``carpet'' as well as word pairings such as ``dirty carpet,'' ``dirty room,'' and ``dirty bathroom.'' Along with complaints about off-putting smells, we could conclude that Western tourists had high expectations about cleanliness when traveling in Japan.

    An interesting detail of the keyword ranking is that the word ``comfortable'' was high on the satisfaction factors and ``uncomfortable'' was high on the dissatisfaction factors. The words were paired with nouns such as ``bed,'' ``room,'' ``pillow,'' and ``mattress,'' when they generally referred to their sleep conditions in the hotel.
    It seems that Western tourists were particularly sensitive about the hotels’ comfort levels and whether they reached their expectations. The ranking for the negative keyword ``uncomfortable'' is similar across most price ranges except the two most expensive ones, where this keyword disappears from the top 10 list.

    Albeit lower in priority, the price range of 15,000 to 20,000 yen hotels also includes ``free'' as one of the top 10 positive keywords, mainly paired with ``Wi-Fi.'' This price range corresponds to business hotels, where users would expect this feature the most.

  \subsection{Tobacco, what is that smell?}\label{disc:tobacco}

    A concern for Western tourists was the smell of tobacco in their room, which can be regarded as a soft attribute. Tobacco was found not only as a standalone word with ``cigarette'' but also in word pairs in Table \ref{tab:adj_en_neg}, such as ``funny smell.'' By manually inspecting a sample of reviews with this keyword, we noticed that the room was often advertised as non-smoking; however, the smell permeated the room and curtains. Another common complaint was that there were no nonsmoking facilities available. The smell of smoke can completely ruin some customers’ stay and thus lead to bad reviews, thereby lowering the number of future customers.

    In contrast, Chinese customers seemed to not be bothered by this. Previous research has stated that 49–60 \% of Chinese men (and 2.0–2.8 \% of women) currently smoke or smoked in the past. This was derived from a sample of 170,000 Chinese adults in 2013–2014, which is high compared to many English-speaking countries \cite[][]{zhang2019tobacco,who2015tobacco}.

    Japan has a polarized view on the topic of smoking. Although it has one of the world’s largest tobacco markets, tobacco use has decreased in recent years. Smoking in public spaces is prohibited in some wards of Tokyo (namely Chiyoda, Shinjuku, and Shibuya). However, it is generally only suggested and not mandatory to lift smoking restrictions in restaurants, bars, hotels, and public areas. However, many places have designated smoking rooms to keep the smoke in an enclosed area and avoid bothering others. Nevertheless, businesses, especially those who cater to certain customers, are generally discouraged by smoking restrictions if they want to maintain their clientele. To cater to all kinds of customers, including Western and Asian, Japanese hotels must provide spaces without tobacco smell. Even if the smoke does not bother a few customers, the lack of such a smell would make it an appropriate space for all customers.

@@

    The hotel's location, closeness to the subway and public transportation, and availability of nearby shops proved to be of importance to both Chinese and English-speaking tourists. In positive word pairings in Tables \ref{tab:adj_zh_pos} and \ref{tab:adj_en_pos}, we can find pairs such as ``\begin{CJK}{UTF8}{gbsn}不错 位置\end{CJK} (nice location),'' ``\begin{CJK}{UTF8}{gbsn}近 地铁站\end{CJK} (near subway station),'' ``\begin{CJK}{UTF8}{gbsn}近 地铁\end{CJK} (near subway)'' in Chinese texts and ``good location,'' ``great location,'' and ``great view'' as well as single keywords ``location'' and ``shopping'' for English speakers, and ``\begin{CJK}{UTF8}{gbsn}交通\end{CJK} (traffic),'' ``\begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping),'' ``\begin{CJK}{UTF8}{gbsn}地铁\end{CJK} (subway),'' and ``\begin{CJK}{UTF8}{gbsn}环境\end{CJK} (environment or surroundings)'' for Chinese speakers. All of these keywords and their location in each population's priorities across the price ranges signify that the hotel's location was a secondary but still important point for their satisfaction. However, since this is a hard attribute, it is not often considered in the literature. By examining examples from the data, we recognized that most customers were satisfied if the hotel was near at least two of the following facilities: subway, train, and convenience stores.

    Japan is a country with a peculiar public transportation system. During rush hour, the subway is crowded with commuters, and trains and subway stations create a confusing public transportation map for a visitor in Tokyo. Buses are also available, albeit less used than rail systems in metropolitan cities. These three means of transportation are usually affordable in price. There are more expensive means, such as the bullet train \textit{shinkansen} for traveling across the country and taxis. The latter is a luxury in Japan compared to other countries, especially in less developed countries, where this is a low-cost choice. In Japan, taxis provide a high-quality experience with a matching price. Therefore, subway availability and maps or GPS applications as well as a plan to travel the city are of utmost necessity for tourists.

    Japanese convenience stores are also famous worldwide, because they offer a wide range of services and products, from drinks and snacks to full meals, copy and scanning machines, alcohol, cleaning supplies, personal hygiene items, underwear, towels, and international ATMs. If some trouble occurs, or a traveler forgot to pack a particular item, it is mostly certain that they can find it.

    Therefore, considering that both transportation systems and nearby shops are points of interest for Chinese and Western tourists, the location of a Japanese hotel must be carefully chosen prior to construction. Although not a top priority, this is a universal factor for both customer groups and is conducive to generate positive reviews.

@@

  In this section, we explore the possible interactions with Japanese hospitality, the differences between perceptions of Chinese and Western tourists as well as the possible causes, variations in perceptions across different price ranges, and the implications for the industry. We also discuss the differences between the hotel's hard and soft attributes and their contributions to customers' satisfaction.

@@

    To date, scholars have been correcting our historical bias towards the West. Studies have determined that different cultural backgrounds lead to different expectations, which influence tourists' satisfaction. In other words, tourists of a particular culture have different leading satisfaction factors across different destinations. However, Japan presents a particular environment; the spirit of hospitality and service, \textit{omotenashi}, excels and is considered to be of the highest standard across the world. Our study explores whether such an environment can affect different cultures equally Or whether it is attractive only to certain cultures.

    Our results indicate that Western tourists are more satisfied with soft attributes, such as friendly and helpful staff in Japan, than Chinese tourists. As explained earlier in this paper, Japan is well known for its customer service. Respectful language and bowing are not exclusive to high-priced hotels or businesses; these are met in convenience stores as well. The level of hospitality, even in the cheapest convenience store, is starkly different from Western culture. Although it could be a cultural shock to some, it is mostly approved. The Japanese staff treats all customers respectfully, and this might be unforeseen by some customers. In higher-priced hotels, the adjectives used to praise the service ranged from normal descriptors like ``good'' to higher levels of praise like ``wonderful staff,'' ``wonderful experience,'' ``excellent service,'' and ``excellent staff.'' Furthermore, \cite{kozak2002} and \cite{shanka2004} have also proven that hospitality and staff friendliness are two determinants of Western tourists' satisfaction.

    However, the negative English keywords indicate that a large part of the dissatisfaction with Japanese hotels stemmed from a lack of hygiene and room cleanliness. Although Chinese customers had solely positive keywords about cleanliness, English-speaking customers deemed many places unacceptable to their standards, particularly hotels with rooms priced below 50,000 yen per night. The most common complaint regarding cleanliness was about the carpet, followed by complaints about cigarette smell and lack of general hygiene. \cite{kozak2002} also proved that hygiene and cleanliness were essential satisfaction determinants for Western tourists. However, in the previous literature, this was linked merely to satisfaction. In contrast, our research revealed that words related to cleanliness were mostly linked to dissatisfaction. We could assert that Westerners had a high standard of room cleanliness compared to their Chinese counterparts.

    According to previous research, Western tourists are already inclined to appreciate hospitality for their satisfaction. When presented with Japanese hospitality, this expectation is met and overcome. In contrast, according to our results, Chinese tourists were more concerned about room quality rather than hospitality, staff, or service. However, when analyzing the word pairs for ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' and ``\begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great),'' we can see that they praise staff, service, and breakfast. By observing the percentage of hard to soft attributes in Figure \ref{fig:hard_soft_zh}, however, we discover that Chinese customers were more satisfied with hard attributes compared to Western tourists, who seemed to be meeting more than their expectations.
